\documentclass[11pt,a4paper,sans]{moderncv}
% ----------------------------------------------------------------------------------
% CONFIGURATION
% ----------------------------------------------------------------------------------
\moderncvstyle{banking} 
\moderncvcolor{blue}    

\usepackage[utf8]{inputenc}
\usepackage[top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}

% Custom Color
\definecolor{color1}{rgb}{0.1, 0.5, 0.9}

% ----------------------------------------------------------------------------------
% HEADER INFORMATION
% ----------------------------------------------------------------------------------
\name{Your}{Name}

\begin{document}

% ----------------------------------------------------------------------------------
% MANUAL ATS-FRIENDLY HEADER
% ----------------------------------------------------------------------------------
\begin{center}
% NAME
{\fontsize{30}{36}\selectfont \textbf{Your Name}}\\[0.5em]

% TITLE
{\fontsize{14}{16}\selectfont \textcolor{color1}{Your Professional Title | Your Specialization}}\\[0.5em]

% CONTACT INFO
{\small
City, Country \ \textbullet \ +1 234 567 8900 \ \textbullet \ 
\href{mailto:your.email@example.com}{your.email@example.com} \ \textbullet \ 
\href{https://www.linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile}}\\[1em]
\end{center}

% ----------------------------------------------------------------------------------
% BODY CONTENT
% ----------------------------------------------------------------------------------

% Professional Summary
\section{\textcolor{color1}{Professional Summary}}
\cvitem{}{
\textbf{Your Professional Title} with X+ years of experience in your field. 
Describe your key expertise, achievements, and what makes you unique. 
Highlight your most impressive metrics and accomplishments.
}

% Technical Skills
\section{\textcolor{color1}{Technical Skills}}
\small{
\textbf{Category 1}{: Technology 1, Technology 2, Technology 3} \\
\textbf{Category 2}{: Technology 4, Technology 5, Technology 6} \\
\textbf{Category 3}{: Technology 7, Technology 8, Technology 9} \\
\textbf{Category 4}{: Technology 10, Technology 11, Technology 12}
}

% Professional Experience
\section{\textcolor{color1}{Professional Experience}}

\cventry{Start Date -- Present}{Job Title}{Company Name}{Location}{}{%
\begin{itemize}%
\item \textbf{Achievement 1:} Describe what you built/achieved with specific metrics and technologies used.
\item \textbf{Achievement 2:} Another accomplishment with quantifiable results.
\item \textbf{Achievement 3:} Focus on impact and business value delivered.
\end{itemize}
}

\cventry{Start Date -- End Date}{Previous Job Title}{Previous Company}{Location}{}{%
\begin{itemize}%
\item \textbf{Achievement 1:} What you accomplished in this role.
\item \textbf{Achievement 2:} Another key contribution.
\item \textbf{Achievement 3:} Impact you made on the organization.
\end{itemize}
}

% Education
\section{\textcolor{color1}{Education}}
\cventry{Start Year -- End Year}{Degree Name}{University Name}{Location}{}{
Focus: Your specialization or key courses
}

% Certifications & Languages
\section{\textcolor{color1}{Certifications \& Languages}}
\cvitem{Certifications}{
\textbf{Certification 1} | 
\textbf{Certification 2} | 
\textbf{Certification 3}
}
\cvitem{Languages}{Language 1 (Level), Language 2 (Level), Language 3 (Level)}

% Community Engagement (Optional)
\section{\textcolor{color1}{Community \& Leadership}}
\cventry{}{Role}{Organization}{Location}{}{
Brief description of your involvement and impact
}

\end{document}
